MultiDataProcessPico

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Removed some extra plots

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/MultiCultiData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"

@@

ProcessData <- ProcessData %>%
  filter(Strain == "SS120" & time >= InitialTime |
         Strain == "MIT9313" |
         Strain =="MED4"  )

@@

```{r prelim ProcessPlot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

@@

ProcessData %>%
  #filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

@@

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()
```

@@

# ProcessData <- ProcessData %>%
#   group_by(Tube) %>%
#    mutate(TrimRollMeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "right", fill = NA),
#           TrimRollMeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "right", fill = NA)
#           ) %>%
#   mutate(DeclineFlagdeltaOD = if_else(time > (time[which.max(TrimRollMeandeltaOD)] + DeclineWindow) & (max(TrimRollMeandeltaOD, na.rm = TRUE) - min(TrimRollMeandeltaOD, na.rm = TRUE)) > deltaODGrowthFlagValue, 1, 0),
#          DeclineFlagOD720 = if_else(time > (time[which.max(TrimRollMeanOD720)] + DeclineWindow) & (max(TrimRollMeanOD720, na.rm = TRUE) - min(TrimRollMeanOD720, na.rm = TRUE)) > OD720GrowthFlagValue, 1, 0)) %>%
#     filter(DeclineFlagdeltaOD == 0,
#            DeclineFlagOD720 == 0) %>%
#   select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
#   ungroup()
# 
# glimpse(ProcessData)

@@

ProcessData %>%
  #filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

@@

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

@@

# Attempt  Fits of Data
Create R function for logistic equation.
Check with Max for alternate formulations that include lag?
Consider which parameter(s) to report for comparison(s) of strain responses to growth conditions
  -mu
  -Pmax
  -other...
```{r fitting functions, message = FALSE}
#define a logistic equation as a function.
#x will be taken from 'time' when we run the fit.
logistic_eqn <- function(x, Lmax, Lmu, Lintercept){(Lmax*Lintercept*exp(Lmu*x))/(Lmax + (Lintercept*(exp(Lmu*x)-1)))}

@@

# bob <- c(1,2,4,5,6,7)
# 
# growth_amp(y = bob)

@@

# As of Dec 2023 all the na_if code are not working so are commented out
```{r nested regressions }

@@

#XXXDoug 16 May 2022XXX
# %>%
#    mutate(IsOD720_GLagNeg = if_else(lognormOD720_GompLag <= 0, 1, 0), # fails here because of Nulls generated line 437
#           IsdeltaOD_GLagNeg = if_else(lognormdeltaOD_GompLag <= 0, 1, 0))
#

@@

```{r test fits}
#Chunk to work out additions of new fit models

# testamp <- ProcessData %>%
#   filter(lognormdeltaOD > 0) %>%
#   filter(lognormOD720 > 0) %>%
# nest(tubedata = c(time,  ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
#   mutate(GrowthAmpdeltaOD = map(tubedata, ~growth_amp(y = .$rollmeandeltaOD)))
#

@@

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  #drop_na(deltaOD_logistic) %>%
  filter(Tube == 6) %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
 mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(OD720trunc_logistic_predict), names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
 # geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05) + 
  #geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max OD720):  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

ProcessDataNestGrowth %>%
  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05) +
  #geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max deltaOD):   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(OD720trunc_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
 # geom_point(aes(x = OD720trunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
 # geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

@@

Compare truncated vs full run 
```{r compare}

ProcessDataNestGrowth %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
 unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720_Trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720_Trunc_Lmu = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720_Trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu)  %>%
  ggplot() +
  geom_point(aes(x = OD720_TimetoMax, y = OD720_Lmu), colour = "Darkgreen", size = 4) +
  #scale_colour_manual(values = MCMIXColours) +
 geom_point(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu), colour = "Red", size = 4) +
ggrepel::geom_text_repel(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
# scale_colour_manual(values = MCMIXColours) +
#   scale_shape_manual(values = c(13, 16)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
#   coord_fixed(ratio = 1) +
#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
  facet_grid(cols = vars(Tube, WL, Strain)) +
  theme_bw() +
  labs(title = "Full and Truncated Logistic Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       x = "Time (h)")

ProcessDataNestGrowth %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
 unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(deltaOD_Trunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
         deltaOD_Trunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
         deltaOD_Trunc_Lmu = deltaODtrunc_logistic_tidied_estimate_Lmu,
         deltaOD_Trunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu)  %>%
  ggplot() +
  geom_point(aes(x = deltaOD_TimetoMax, y = deltaOD_Lmu), colour = "Darkgreen", size = 4) +
  #scale_colour_manual(values = MCMIXColours) +
 geom_point(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu), colour = "Red", size = 4) +
ggrepel::geom_text_repel(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
# scale_colour_manual(values = MCMIXColours) +
#   scale_shape_manual(values = c(13, 16)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
#   coord_fixed(ratio = 1) +
#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
  facet_grid(cols = vars(Tube, WL, Strain)) +
  theme_bw() +
  labs(title = "Full and Truncated Logistic Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       x = "Time (h)")

>>>>

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"

@@

# ProcessData <- ProcessData %>%
#   filter(Strain == "SS120" & time >= InitialTime |
#          Strain == "MIT9313" |
#          Strain =="MED4"  )

@@

```{r prelim ProcessPlot}

@@

@@

@@

ProcessData <- ProcessData %>%
  group_by(Tube) %>%
   mutate(TrimRollMeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "right", fill = NA),
          TrimRollMeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "right", fill = NA)
          ) %>%
  mutate(DeclineFlagdeltaOD = if_else(time > (time[which.max(TrimRollMeandeltaOD)] + DeclineWindow) & (max(TrimRollMeandeltaOD, na.rm = TRUE) - min(TrimRollMeandeltaOD, na.rm = TRUE)) > deltaODGrowthFlagValue, 1, 0),
         DeclineFlagOD720 = if_else(time > (time[which.max(TrimRollMeanOD720)] + DeclineWindow) & (max(TrimRollMeanOD720, na.rm = TRUE) - min(TrimRollMeanOD720, na.rm = TRUE)) > OD720GrowthFlagValue, 1, 0)) %>%
    filter(DeclineFlagdeltaOD == 0,
           DeclineFlagOD720 == 0) %>%
  select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
  ungroup()

@@

@@

@@

# Fits of Data
Create R function for logistic equation.
```{r fitting functions, message = FALSE}
#define a logistic equation as a function.
#x will be taken from 'time' when we run the fit.
logistic_eqn <- function(x, Lmax, Lmu, Lintercept){(Lmax*Lintercept*exp(Lmu*x))/(Lmax + (Lintercept*(exp(Lmu*x)-1)))}

@@

@@

```{r nested regressions }

@@

@@

@@

# ProcessDataNestGrowth %>%
#   filter(Tube == 5) %>%
#   mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
#   unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
#   ggplot() +
#   geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
#   scale_colour_manual(values = MCMIXColours) +
#   geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
#   geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
#   geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
#   #coord_cartesian(xlim = c(0, 675)) +
#   #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
#   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
#   annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
#   annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
#   annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
#   annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
#   labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
#   theme_bw() +
#   labs(colour = "Actinic PAR (nm)") +
#   guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

@@
